%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Full-Stack Software Engineer} % Job title
{Ford Motor Company } % Organization
{Taylor, MI} % Location
{Feb 2018 - Present} { }% Date(s)
\vskip -4.5mm
\cventry
{Back End Notes} {}{} {} % Sub heading for full stack ***** dont delete these empty brackets, \cventry needs 5 of these.
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built microservices for storing software, managing applications and application-software relationships and dependencies, performing updates to applications and software, and releasing applications and software for use in vehicles.}
\item {Created service to produce valid test files of user-specified sizes with parsable headers.}
\item {Developed methods to parse file headers and stream the files accordingly to different endpoints.}
\item {Set up flagging system to determine required attributes of files for front-end editing and release.}
\item {Implemented process for updating files based on versioning using a software differential generator to reduce software update times.}
\end{cvitems}
}
\vskip -0.5mm
\cventry
{Front End Notes} {}{} {} % Sub heading for full stack ***** dont delete these empty brackets, \cventry needs 5 of these.
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built UI for managing storage, packaging, dependencies, and delivery of software and software updates.}
\item {Improved consistency across UI by componentizing features used in multiple locations to be utilized globally, implementing modes to allow for location-based behavior and display differences.}
\item {Improved performance/page and element loading by implementing selectable tables using lazy loading to replace performance-heavy drop-downs.}
\item {Designed and implemented selectable tiles with selected, active, and disabled modes.}
\item {Created directives to allow for in-line editing.}
\item {Reduced network call lag using results paging.}
\end{cvitems}
}
\vskip -0.5mm
\cventry
{DevOps Notes} {}{} {} % Sub heading for full stack ***** dont delete these empty brackets, \cventry needs 5 of these.
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Programmed automated deployment pipeline to perform blue-green deploys, with gateways for engineer-triggered green deploys to the dev, qa, and performance environments and product manager-triggered green deploys to the prod environment, with automatically triggered blue-green swaps and re-routing.}
\item {Built Splunk dashboard for application monitoring, such as network call monitoring, user-specific activity, file analytics, and error tracking, using regex to parse desired tracking fields from logs.}
\item {Automated deploys of applications/services to Pivotal Cloud Foundry through Jenkins, including stages such as builds, unit testing, integration/contract testing, and gateways to trigger those builds.}
\item {Built pipeline for setting up environments and user access in Pivotal Cloud Foundry.}
\end{cvitems}
}


%------------------------------------------------    
\vskip 2mm
\cventry
{Automantion Engineer} % Job title
{Ministry Brands - ParishSOFT} % Organization
{Ann Arbor, MI} % Location
{June. 2016 - Dec. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and Developed automated regression test suites using Java and Python-based Selenium for microservice deployments.}
\item {Wrote JUnit tests to maintain 90 - 95 percent code coverage.}
\item {Presented optimization reports in DevOps meetings to target performance weaknesses and improve user experience through suggested enhancements
.}
\end{cvitems}
}

%------------------------------------------------
\cventry
{IT Technician} % Job title
{Eastern Michigan University} % Organization
{Ypsilanti, MI} % Location
{Feb. 2012 - April. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Provided support and assistance for classroom computers and equipment.}
\item {Performed malware removal and hardware support for university-issued computers.}
\item {Performed software maintenance and reimagining of lab computers and rented/faculty laptops.}
\end{cvitems} 
}
\end{cventries}
\vspace{-5pt}